The Blessing of FedAvg's Linear Speedup in Federated Learning

### 2020-05-31 source/sec_intro.tex
Update sec_intro.tex

\textbf{Notations}
Throughout the paper, we adopt the following notation. Let $N$ be the total
number of local devices, and $K \leq N$ is the maximal number of devices
that are accessible to the central server.  Let $T$ be the total number of  Stochastic Gradient Descent (SGD) performed on each local device, $E$ be the local steps between two communication steps. Thus, $\frac{T}{E}$ is
the number of communications.

% Our contributions
\subsection{Contributions}
This work focus on providing comprehensive convergence analysis
of FedAvg and accelerated variants under the realistic setting, showing
the less number of communication round is needed to converge to the
target accuracy and preserving the linear speedup at the same time.
More specifically, for strongly convex and smooth problems, we provide the {\small{$\cO(\frac{1}{NT})$}} convergence  for FedAvg and the local steps can be as large as {\small{$\cO(\sqrt{\frac{T}{N}})$}}. For convex and smooth objectives, we prove the {\small{$\cO(\sqrt{\frac{1}{NT}})$}} and the local steps can be as large as {\small{$\cO(\sqrt{\frac{T}{N}})$}}. The same conclusions can be equally applied for Nesterov accelerated FedAvg. To the best of our knowledge, this is the first linear speedup results for FedAvg with Nesterov accelerated SGD. Furthermore, 
we also provide the first improved convergence rate for Nesterov accelerated FedAvg comparing to FedAvg under a popular overparamterized setting. 
Last but not least, we systematically examine the convergence rate of
FedAvg and it accelerated variants on both a real-world dataset and a synthetic dataset. The empirical observations are well-aligned with theoretical indications.

>>>>

\textbf{Notations}
Throughout the paper, we adopt the following notations. Let $N$ be the total
number of local devices, and $K \leq N$ is the maximal number of devices
that are accessible to the central server.  Let $T$ be the total number of  Stochastic Gradient Descent (SGD) performed on each local device, $E$ be the local steps between two communication steps. Thus, $\frac{T}{E}$ is
the number of communications.

% Our contributions
\subsection{Contributions}
This work focus on providing comprehensive convergence analysis
of FedAvg and accelerated variants under the realistic setting, showing
the less number of communication round is needed to converge to the
target accuracy and preserving the linear speedup at the same time.
More specifically, for strongly convex and smooth problems, we provide the {\small{$\cO(\frac{1}{NT})$}} convergence  for FedAvg and the local steps can be as large as {\small{$\cO(\sqrt{\frac{T}{N}})$}}. For convex and smooth objectives, we prove the {\small{$\cO(\frac{1}{\sqrt{NT}})$}} and the local steps can be as large as {\small{$\cO(\sqrt{\frac{T}{N}})$}}. The same conclusions can be equally applied for Nesterov accelerated FedAvg. To the best of our knowledge, this is the first linear speedup results for FedAvg with Nesterov accelerated SGD. Furthermore, 
we also provide the first improved convergence rate for Nesterov accelerated FedAvg comparing to FedAvg under a popular overparamterized setting. 
Last but not least, we systematically examine the convergence rate of
FedAvg and it accelerated variants on both a real-world dataset and a synthetic dataset. The empirical observations are well-aligned with theoretical indications.
